Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-16 ms.tex
caption

\begin{figure}
\begin{center}
\epsfig{file=tcomparison.eps, width=3.3in}
\caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
model $T_2$, and \cite{planckdust} temperature (labeled $T_{R1.20}$). Note the differing colorscales.
Both models incorporating \PLANCK~data clearly show a major improvement in 
resolution relative to SFD.}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\epsfig{file=tcomparison.eps, width=3.3in}
\caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
model $T_2$, and \cite{planckdust} temperature (labeled $T_{R1.20}$) for a
 $10.5^{\circ}\times8.3^{\circ}$  region centered about 
$(l,b) = (111.6^{\circ}, 20.3^{\circ})$. Note the 
differing colorscales. Both models incorporating \PLANCK~data clearly show a 
major improvement in angular resolution relative to SFD.}
\end{center}
\end{figure}
